---
title: "NGA multicountry report"
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-location: left
    page-layout: full
    self-contained: true
editor: source
params:
  parameters_name: NULL
---



```{r, include=FALSE}

# Load options and config -------------------------------------------------------------
source("0_options.R")
config <- yaml::read_yaml("study_config.yml") # config file with all parameters


# Load processed data -------------------------------------------------------------
readRDS(file.path(config$data_processed, paste0("inputs_",opt$country,"_20_2020-12-25_to_2021-09-17.rds"))) -> inputs     # LOAD NAMES CORRECTLY 
readRDS(file.path(config$data_processed, paste0("results_",opt$country,"_20_2020-12-25_to_2021-09-17.rds"))) -> results      
readRDS(file.path(config$data_processed, paste0("periods_",opt$country,"_20_2020-12-25_to_2021-09-17.rds"))) -> periods 

# Graphical parameters -------------------------------------------------------------
pal=  c("#FFF2B2",
        "#FFD772",
        "#F9B74C",
        "#DFA144",
        "#A6B96A",
        "#6FAF91",
        "#4F9FAE",
        "#2B7F8E")

social_palette <- c(
"#E07B54",  # warm terracotta
"#4A7BB7",  # professional blue
"#F2C14E",  # golden yellow
"#7B9E87",  # muted sage green
"#C47DB5",  # soft purple
"#A0A0A0"   # neutral grey
)
```


- **Country:** `r aux_country`
- **Timeframe:** `r min(periods$start)` to `r max(periods$end)` (`r max(periods$period)`, 2-week periods)
- **Sampling:** `r config$study$n_sample` samples per period

# Inputs

## Sample mean contact matrices
::: {.panel-tabset}

### Overall

```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_total[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_long$from)
cm_long <- cm_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_summary <- cm_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap <- function(df) {
  df %>%
    ggplot(aes(x = to, y = from, fill = m)) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = "#1565C0", name = "Mean contacts") +
    facet_wrap(~ period, ncol = 5, labeller = label_both) +
    labs(title = "CM — Mean", x = "", y = "") +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1),
      strip.background = element_rect(fill = "grey90", color = NA),
      panel.grid       = element_blank()
    )
}
plot_cm_heatmap(cm_summary)

```


### Home
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_home_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_home[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_home_long$from)
cm_home_long <- cm_home_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_home_summary <- cm_home_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_home_summary) + labs(title = "Home CM — Mean")
```


### School
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_school_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_school[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_school_long$from)
cm_school_long <- cm_school_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_school_summary <- cm_school_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_school_summary) + labs(title = "School CM — Mean")
```


### Work
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_work_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_work[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_work_long$from)
cm_work_long <- cm_work_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_work_summary <- cm_work_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_work_summary) + labs(title = "Work CM — Mean")
```

### Transport
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_transport_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_transport[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_transport_long$from)
cm_transport_long <- cm_transport_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_transport_summary <- cm_transport_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_transport_summary) + labs(title = "Transport CM — Mean")
```

### Leisure
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_leisure_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_leisure[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_leisure_long$from)
cm_leisure_long <- cm_leisure_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_leisure_summary <- cm_leisure_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_leisure_summary) + labs(title = "Leisure CM — Mean")
```

### Other
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_other_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_other[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_other_long$from)
cm_other_long <- cm_other_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_other_summary <- cm_other_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_other_summary) + labs(title = "Other CM — Mean")
```

:::




## Standard deviation contact matrices
:::{.panel-tabset}
### Overall
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd <- function(df) {
  df %>%
    ggplot(aes(x = to, y = from, fill = sdt)) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = "orange", name = "sd contacts") +
    facet_wrap(~ period, ncol = 5, labeller = label_both) +
    labs(title = "CM — sd", x = "", y = "") +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1),
      strip.background = element_rect(fill = "grey90", color = NA),
      panel.grid       = element_blank()
    )
}
plot_cm_heatmap_sd(cm_summary)
```

### Home 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_home_summary) + labs(title = "Home CM — sd")
```

### School
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_school_summary) + labs(title = "School CM — sd")
```

### Work
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_work_summary) + labs(title = "Work CM — sd")
```

### Transport
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_transport_summary) + labs(title = "Transport CM — sd")
```

### Leisure
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_leisure_summary) + labs(title = "Leisure CM — sd")
```

### Other
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_other_summary) + labs(title = "Other CM — sd")
```
:::

::: {.panel-tabset}

### Rt over time
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract rt
rt_long <- map_dfr(1:opt$nperiods, function(p){
    rt <- inputs[[p]]$rt
    as.data.frame(rt) %>%
      mutate(period = p)
})

# plot rt
rt_long %>%
  ggplot(aes(x = period, y = rt)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_x_continuous(breaks = 1:opt$nperiods) +
  labs(title = "Rt over time", x = "Period", y = "Rt") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())

```

### Contact weights over time
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
w_long <- map_dfr(1:opt$nperiods, function(p){
    w <- inputs[[p]]$weights
    as.data.frame(w) %>%
      mutate(period = p)
})

# plot weights
w_long %>%
  ggplot(aes(x = period, y = w)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:opt$nperiods) +
  labs(title = "Contact weights over time", x = "Period", y = "weights") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())

```


### Incidence by age group over time
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract incidence
incidence_long <- map_dfr(1:opt$nperiods, function(p){ 
    incidence <- inputs[[p]]$incidence
    as.data.frame(incidence) %>%
      mutate(period = p)
})

# plot incidence
incidence_long %>% 
  ggplot(aes(x = period, y = rel_incidence, group = agegroup, color = agegroup)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:opt$nperiods) +
  scale_color_manual(values = pal) +
  scale_fill_manual(values = pal) +
  labs(title = "Relative incidence by age group over time", x = "Period", y = "relative incidence") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())

```


:::

# Results


## Sample mean NGM and setting-specific transmission matrices
::: {.panel-tabset}

### Next Generation Matrix

```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# Extract ngm into a long data frame
ngm_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_long$from)
ngm_long <- ngm_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_summary <- ngm_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_ngm_heatmap <- function(df) {
  df %>%
    ggplot(aes(x = to, y = from, fill = m)) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = "#1565C0", name = "mean nr of infections") +
    facet_wrap(~ period, ncol = 5, labeller = label_both) +
    labs(title = "NGM — mean", x = "", y = "") +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1),
      strip.background = element_rect(fill = "grey90", color = NA),
      panel.grid       = element_blank()
    )
}
plot_ngm_heatmap(ngm_summary)
```

### Home
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_long_home <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_HOME"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_long_home$from)
ngm_long_home <- ngm_long_home %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_home_summary <- ngm_long_home %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_home_summary) + labs(title = "Home transmission matrix — mean")
```

### School
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_long_school <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_SCHOOL"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_long_school$from)
ngm_long_school <- ngm_long_school %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_school_summary <- ngm_long_school %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_school_summary) + labs(title = "School transmission matrix — mean")
```

### Work
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_long_work <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_WORK"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_long_work$from)
ngm_long_work <- ngm_long_work %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_work_summary <- ngm_long_work %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_work_summary) + labs(title = "Work transmission matrix — mean")
```

### Transport 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_transport_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_TRANSPORT"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_transport_long$from)
ngm_transport_long <- ngm_transport_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_transport_summary <- ngm_transport_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_transport_summary) + labs(title = "Transport transmission matrix — mean")
```

### Leisure
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_leisure_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_LEISURE"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_leisure_long$from)
ngm_leisure_long <- ngm_leisure_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_leisure_summary <- ngm_leisure_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_leisure_summary) + labs(title = "Leisure transmission matrix — mean")
```

### Other
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_other_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_OTHER"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_other_long$from)
ngm_other_long <- ngm_other_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_other_summary <- ngm_other_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_other_summary) + labs(title = "Other transmission matrix — mean")
```

:::

## Standard deviation NGM and setting-specific transmission matrices
::: {.panel-tabset}
### Next Generation Matrix

```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd <- function(df) {
  df %>%
    ggplot(aes(x = to, y = from, fill = sdt)) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = "orange", name = "nr of infections sd") +
    facet_wrap(~ period, ncol = 5, labeller = label_both) +
    labs(title = "NGM — sd", x = "", y = "") +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1),
      strip.background = element_rect(fill = "grey90", color = NA),
      panel.grid       = element_blank()
    )
}
plot_ngm_heatmap_sd(ngm_summary)
```

### Home 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_home_summary) + labs(title = "Home transmission matrix — sd")
```

### School 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_school_summary) + labs(title = "School transmission matrix — sd")
```

### Work 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_work_summary) + labs(title = "Work transmission matrix — sd")
```

### Transport
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_transport_summary) + labs(title = "Transport transmission matrix — sd")
```

### Leisure
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_leisure_summary) + labs(title = "Leisure transmission matrix — sd")
```

### Other
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_other_summary) + labs(title = "Other transmission matrix — sd")
```
:::

## Elasticity and sensitivity matrices
::: {.panel-tabset}
```{r, echo=FALSE}
# ── Helper: extract sensitivity and elasticity matrices ──────────────────
extract_special_matrix <- function(result_name) {
  map_dfr(1:opt$nperiods, function(p){
    map_dfr(1:config$study$n_sample, function(s){
      mat <- results[[p]][[result_name]][[s]]
      rownames(mat) <- config$study$age_groups
      colnames(mat) <- config$study$age_groups
      age_labels = rownames(mat)
      as.data.frame(mat) %>%
        mutate(from = age_labels) %>%
        pivot_longer(-from, names_to = "to", values_to = "value") %>%
        mutate(period = p, sample = s)
      })
    })
}



# ── Summary ───────────────────────────────────────────────────────────────────
summarise_special_matrix <- function(df) {
  df %>%
    group_by(period, from, to) %>%
    summarise(
      m = mean(value, na.rm = TRUE),
      sdt   = sd(value, na.rm = TRUE),
      .groups = "drop"
    )
}



# ── Plot helper ───────────────────────────────────────────────────────────────
plot_special_matrix <- function(df, fill_var,title, color) {
  df %>%
    ggplot(aes(x = to, y = from, fill = {{ fill_var }})) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = color, name = "") +
    facet_wrap(~ period, ncol = 5, labeller = label_both) +
    labs(title = title, x = "", y = "") +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1),
      strip.background = element_rect(fill = "grey90", color = NA),
      panel.grid       = element_blank()
    )
}
```


### Elasticity matrix - mean
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract
elas_long = extract_special_matrix("elas")
#summary
elas_summary = summarise_special_matrix(elas_long)
#plot
plot_special_matrix(elas_summary, m, "Elasticity matrix — mean","#1565C0")
```


### Sensitivity matrix - mean
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract
sens_long = extract_special_matrix("sens")
#summary
sens_summary = summarise_special_matrix(sens_long)
#plot
plot_special_matrix(sens_summary, m, "Sensitivity matrix — mean", "#1565C0")
```

### Elasticity matrix - sd
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
plot_special_matrix(elas_summary, sdt, "Elasticity matrix — sd","orange")
```


### Sensitivity matrix - sd
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
plot_special_matrix(sens_summary, sdt, "Sensitivity matrix — sd", "orange")
```

:::

## Overall cumulative elasticity, setting-specific cumulative elasticity, Dominant eigenvalue (Rt), right eigenvector (relative incidence) and q-susceptibility
::: {.panel-tabset}

```{r}
# ── Helper: extract any vector of results (e.g., q-susceptibility, cumulative elasticity)───────────────
extract_vector <- function(result_name, element_labels) {
  map_dfr(1:opt$nperiods, function(p) {
    map_dfr(1:config$study$n_sample, function(s) {
      vec <- results[[p]][[result_name]][[s]]
      tibble(
        period  = p,
        sample  = s,
        element = factor(element_labels, levels = element_labels),
        value   = vec
      )
    })
  })
}

# ── Summary helper ───────────────────────────────────────────────────────────────
summarise_vector <- function(df) {
  df %>%
    group_by(period, element) %>%
    summarise(
      median  = median(value, na.rm = TRUE),
      p2.5  = quantile(value, 0.025, na.rm = TRUE),
      p97.5 = quantile(value, 0.975, na.rm = TRUE),
      .groups = "drop"
    )
}

# ── Plot helper ───────────────────────────────────────────────────────────────
plot_vector_summary <- function(df, title) {
  df %>%
    ggplot(aes(x = period, y = median, group = element, color = element, fill = element)) +
    geom_ribbon(aes(ymin = p2.5, ymax = p97.5), alpha = 0.2, color = NA) +
    #geom_errorbar(aes(ymin = p2.5, ymax = p97.5), width = 0.7,linewidth = 0.8) +
    geom_line(linewidth = 0.8) +
    geom_point(size = 1.5) +
    scale_x_continuous(breaks = 1:opt$nperiods) +
    scale_color_manual(values = pal) +
    scale_fill_manual(values = pal) +
    labs(
      title = title,
      x     = "Period",
      y     = "Value",
      color = "",
      fill  = ""
    ) +
    theme_minimal(base_size = 11) +
    theme(
      panel.grid.minor = element_blank(),
      legend.position  = "bottom"
    )
}
```


### Cumulative elasticity
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract cumulative elasticity
cum_elasti_long <- extract_vector("cum_elasti", config$study$age_groups)

# summaries
cum_elasti_summary <- summarise_vector(cum_elasti_long)

#plot
plot_vector_summary(cum_elasti_summary, "cum_elasti — Median with 95% CI across samples")
```

### Setting-specific cumulative elasticity
```{r , echo = FALSE,message=FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract setting-specific cumulative elasticity
cum_elasti_set_long <- extract_vector("elas_set", names(results$`1`$elas_set[[1]]))
# summaries
elas_set_summary <- summarise_vector(cum_elasti_set_long)
#plot
plot_vector_summary(elas_set_summary, "cum_elas_set — Median with 95% CI across samples")+
  scale_color_manual(values = social_palette) +
  scale_fill_manual(values = social_palette)
```

### Rt (dominant eigenvalue of NGM)
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract rt
rt_ngm_long <- map_dfr(1:opt$nperiods, function(p){
                map_dfr(1:config$study$n_sample, function(s) {
                    rt <- results[[p]]$eigen[[s]]$value
                    tibble(
                        period = p,
                        sample = s,
                        rt = rt
                    )
                })
})



# check if Rt is the same across samples
table(round(rt_ngm_long$rt,6),rt_ngm_long$period) # similar at 6 decimals, so we can just take the first sample for each period
rt_long_f <- rt_ngm_long %>% group_by(period) %>%
  slice(1) %>%
  ungroup()

# # confirm that this matches the rt from inputs
# all(round(rt_long$rt,4)==round(rt_long_f$rt,4)) # matches perfectly

rt_long_f$sample=NULL

# plot rt
rt_long_f %>%
  ggplot(aes(x = period, y = rt)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_x_continuous(breaks = 1:opt$nperiods) +
  labs(title = "Dominant eigenvalue over time (Rt)", x = "Period", y = "Rt") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())
```

### Right eigenvector (relative incidence by age group)
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract right eigenvector
w_long <-map_dfr(1:opt$nperiods, function(p) {
                  map_dfr(1:config$study$n_sample, function(s) {
                    vec <- results[[p]]$eigen[[s]]$w
                    tibble(
                      period  = p,
                      sample  = s,
                      element = factor(config$study$age_groups, levels = config$study$age_groups),
                      value   = vec
      )
    })
  })
# # check that w sums to 1
# w_long %>%
#   group_by(period, sample) %>%
#   summarise(sum_w = sum(value)) # sums to 1 for all samples and periods 
# # checks out

# plot w
w_long %>% 
  ggplot(aes(x = period, y = value, group = element, color = element)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:opt$nperiods) +
  scale_color_manual(values = pal) +
  scale_fill_manual(values = pal) +
  labs(title = "Right eigenvector (relative incidence)", x = "Period", y = "Relative Incidence") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())

```

### Q-susceptibility
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract q-susceptibility
q_susc_long     <- extract_vector("q_susc",     config$study$age_groups)

# summaries
q_susc_summary   <- summarise_vector(q_susc_long)

#plot
plot_vector_summary(q_susc_summary,     "q_susc — Median with 95% CI across samples")
```
:::

```{r}
# compile and save necessary information for analysis: rt_long_f, elas_set_summary and cum_elas_summary
rt_long_f 
elas_set_summary$element = fct_relabel(elas_set_summary$element, ~ str_sub(.x, 3))
elas_set_summary %>% select(-p2.5, -p97.5) %>% pivot_wider(names_from = element, values_from = c(median)) -> elas_set_summary_wide
# test to see how closer the medians are to 1
elas_set_summary %>% 
  group_by(period) %>%
  summarise(sum(median)) # very good

cum_elasti_summary %>% select(-p2.5, -p97.5) %>% pivot_wider(names_from = element, values_from = c(median)) -> cum_elasti_summary_wide
# test to see how closer the medians are to 1
cum_elasti_summary %>% 
  group_by(period) %>%
  summarise(sum(median)) # very good

results_summary <- rt_long_f %>%
  left_join(elas_set_summary_wide, by = "period") %>%
  left_join(cum_elasti_summary_wide, by = "period")
# save final summary as RDS file
out_file_results_summary <- file.path(config$results_path,paste0("result_summary_",opt$country,"_",max(periods$period),"_",min(periods$start),"_to_",max(periods$start),".rds"))
saveRDS(results_summary, file = out_file_results_summary)
```

