---
title: "NGA multicountry report"
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-location: left
    page-layout: full
    self-contained: true
editor: source
params:
  parameters_name: NULL
---



```{r, include=FALSE}

# Load options and config -------------------------------------------------------------
source("0_options.R")
config <- yaml::read_yaml("study_config.yml") # config file with all parameters


# Load processed data -------------------------------------------------------------
readRDS(file.path(config$data_processed, paste0("inputs_",opt$country,"_20_2020-12-25_to_2021-09-17.rds"))) -> inputs     # LOAD NAMES CORRECTLY 
readRDS(file.path(config$data_processed, paste0("results_",opt$country,"_20_2020-12-25_to_2021-09-17.rds"))) -> results      
readRDS(file.path(config$data_processed, paste0("periods_",opt$country,"_20_2020-12-25_to_2021-09-17.rds"))) -> periods 

# Graphical parameters -------------------------------------------------------------
pal=  c("#FFF2B2",
        "#FFD772",
        "#F9B74C",
        "#DFA144",
        "#A6B96A",
        "#6FAF91",
        "#4F9FAE",
        "#2B7F8E")
```


- **Country:** `r aux_country`
- **Timeframe:** `r min(periods$start)` to `r max(periods$end)` (`r max(periods$period)`, 2-week periods)
- **Sampling:** `r config$study$n_sample` samples per period

# Inputs

## Sample mean contact matrices
::: {.panel-tabset}

### Overall

```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_total[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_long$from)
cm_long <- cm_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_summary <- cm_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap <- function(df) {
  df %>%
    ggplot(aes(x = to, y = from, fill = m)) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = "#1565C0", name = "Mean contacts") +
    facet_wrap(~ period, ncol = 5, labeller = label_both) +
    labs(title = "CM — Mean", x = "", y = "") +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1),
      strip.background = element_rect(fill = "grey90", color = NA),
      panel.grid       = element_blank()
    )
}
plot_cm_heatmap(cm_summary)

```


### Home
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_home_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_home[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_home_long$from)
cm_home_long <- cm_home_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_home_summary <- cm_home_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_home_summary) + labs(title = "Home CM — Mean")
```


### School
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_school_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_school[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_school_long$from)
cm_school_long <- cm_school_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_school_summary <- cm_school_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_school_summary) + labs(title = "School CM — Mean")
```


### Work
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_work_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_work[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_work_long$from)
cm_work_long <- cm_work_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_work_summary <- cm_work_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_work_summary) + labs(title = "Work CM — Mean")
```

### Transport
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_transport_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_transport[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_transport_long$from)
cm_transport_long <- cm_transport_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_transport_summary <- cm_transport_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_transport_summary) + labs(title = "Transport CM — Mean")
```

### Leisure
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_leisure_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_leisure[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_leisure_long$from)
cm_leisure_long <- cm_leisure_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_leisure_summary <- cm_leisure_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_leisure_summary) + labs(title = "Leisure CM — Mean")
```

### Other
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# extract contact matrices
cm_other_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- inputs[[p]]$contacts$matrix_sample_other[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(cm_other_long$from)
cm_other_long <- cm_other_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
cm_other_summary <- cm_other_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_cm_heatmap(cm_other_summary) + labs(title = "Other CM — Mean")
```

:::




## Standard deviation contact matrices
:::{.panel-tabset}
### Overall
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd <- function(df) {
  df %>%
    ggplot(aes(x = to, y = from, fill = sdt)) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = "orange", name = "sd contacts") +
    facet_wrap(~ period, ncol = 5, labeller = label_both) +
    labs(title = "CM — sd", x = "", y = "") +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1),
      strip.background = element_rect(fill = "grey90", color = NA),
      panel.grid       = element_blank()
    )
}
plot_cm_heatmap_sd(cm_summary)
```

### Home 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_home_summary) + labs(title = "Home CM — sd")
```

### School
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_school_summary) + labs(title = "School CM — sd")
```

### Work
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_work_summary) + labs(title = "Work CM — sd")
```

### Transport
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_transport_summary) + labs(title = "Transport CM — sd")
```

### Leisure
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_leisure_summary) + labs(title = "Leisure CM — sd")
```

### Other
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_cm_heatmap_sd(cm_other_summary) + labs(title = "Other CM — sd")
```
:::

::: {.panel-tabset}

### Rt over time
```{r, echo = FALSE}
# extract rt
rt_long <- map_dfr(1:opt$nperiods, function(p){
    rt <- inputs[[p]]$rt
    as.data.frame(rt) %>%
      mutate(period = p)
})

# plot rt
rt_long %>%
  ggplot(aes(x = period, y = rt)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_x_continuous(breaks = 1:opt$nperiods) +
  labs(title = "Rt over time", x = "Period", y = "Rt") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())

```

### Contact weights over time
```{r, echo = FALSE}
w_long <- map_dfr(1:opt$nperiods, function(p){
    w <- inputs[[p]]$weights
    as.data.frame(w) %>%
      mutate(period = p)
})

# plot weights
w_long %>%
  ggplot(aes(x = period, y = w)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:opt$nperiods) +
  labs(title = "Contact weights over time", x = "Period", y = "weights") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())

```


### Incidence by age group over time
```{r, echo = FALSE}
# extract incidence
incidence_long <- map_dfr(1:opt$nperiods, function(p){ 
    incidence <- inputs[[p]]$incidence
    as.data.frame(incidence) %>%
      mutate(period = p)
})

# plot incidence
incidence_long %>% 
  ggplot(aes(x = period, y = rel_incidence, group = agegroup, color = agegroup)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:opt$nperiods) +
  scale_color_manual(values = pal) +
  scale_fill_manual(values = pal) +
  labs(title = "Incidence by age group over time", x = "Period", y = "Incidence") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())

```


:::

# Results


## Sample mean NGM and setting-specific transmission matrices
::: {.panel-tabset}

### Next Generation Matrix

```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# Extract ngm into a long data frame
ngm_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm[[s]]
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_long$from)
ngm_long <- ngm_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_summary <- ngm_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

# plot
plot_ngm_heatmap <- function(df) {
  df %>%
    ggplot(aes(x = to, y = from, fill = m)) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = "#1565C0", name = "mean nr of infections") +
    facet_wrap(~ period, ncol = 5, labeller = label_both) +
    labs(title = "NGM — mean", x = "", y = "") +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1),
      strip.background = element_rect(fill = "grey90", color = NA),
      panel.grid       = element_blank()
    )
}
plot_ngm_heatmap(ngm_summary)
```

### Home
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_long_home <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_HOME"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_long_home$from)
ngm_long_home <- ngm_long_home %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_home_summary <- ngm_long_home %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_home_summary) + labs(title = "Home transmission matrix — mean")
```

### School
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_long_school <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_SCHOOL"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_long_school$from)
ngm_long_school <- ngm_long_school %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_school_summary <- ngm_long_school %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_school_summary) + labs(title = "School transmission matrix — mean")
```

### Work
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_long_work <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_WORK"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_long_work$from)
ngm_long_work <- ngm_long_work %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_work_summary <- ngm_long_work %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_work_summary) + labs(title = "Work transmission matrix — mean")
```

### Transport 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_transport_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_TRANSPORT"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_transport_long$from)
ngm_transport_long <- ngm_transport_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_transport_summary <- ngm_transport_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_transport_summary) + labs(title = "Transport transmission matrix — mean")
```

### Leisure
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_leisure_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_LEISURE"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_leisure_long$from)
ngm_leisure_long <- ngm_leisure_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_leisure_summary <- ngm_leisure_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_leisure_summary) + labs(title = "Leisure transmission matrix — mean")
```

### Other
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
ngm_other_long <- map_dfr(1:opt$nperiods, function(p) {
  map_dfr(1:config$study$n_sample, function(s) {
    mat <- results[[p]]$ngm_set[[s]][["NGM_OTHER"]]
    rownames(mat) <- config$study$age_groups
    colnames(mat) <- config$study$age_groups
    age_labels = rownames(mat)
    as.data.frame(mat) %>%
      mutate(from = age_labels) %>%
      pivot_longer(-from, names_to = "to", values_to = "value") %>%
      mutate(period = p, sample = s)
  })
})
age_labels = unique(ngm_other_long$from)
ngm_other_long <- ngm_other_long %>% mutate(from = factor(from, levels = age_labels),
                to = factor(to, levels = age_labels)) 

# compute statistics 
ngm_other_summary <- ngm_other_long %>%
  group_by(period, from, to) %>%
  summarise(
    m = mean(value, na.rm = TRUE),
    sdt   = sd(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(label = paste0(round(m, 2), " ± ", round(sdt, 2)))

plot_ngm_heatmap(ngm_other_summary) + labs(title = "Other transmission matrix — mean")
```

:::

## Standard deviation NGM and setting-specific transmission matrices
::: {.panel-tabset}
### Next Generation Matrix

```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd <- function(df) {
  df %>%
    ggplot(aes(x = to, y = from, fill = sdt)) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = "orange", name = "nr of infections sd") +
    facet_wrap(~ period, ncol = 5, labeller = label_both) +
    labs(title = "NGM — sd", x = "", y = "") +
    theme_minimal(base_size = 11) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1),
      strip.background = element_rect(fill = "grey90", color = NA),
      panel.grid       = element_blank()
    )
}
plot_ngm_heatmap_sd(ngm_summary)
```

### Home 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_home_summary) + labs(title = "Home transmission matrix — sd")
```

### School 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_school_summary) + labs(title = "School transmission matrix — sd")
```

### Work 
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_work_summary) + labs(title = "Work transmission matrix — sd")
```

### Transport
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_transport_summary) + labs(title = "Transport transmission matrix — sd")
```

### Leisure
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_leisure_summary) + labs(title = "Leisure transmission matrix — sd")
```

### Other
```{r , echo = FALSE, fig.width=10, fig.height=8, fig.dpi=300}
# plot
plot_ngm_heatmap_sd(ngm_other_summary) + labs(title = "Other transmission matrix — sd")
```


:::