---
title: "NGA multicountry validation report"
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-location: left
    page-layout: full
    self-contained: true
editor: source
params:
  parameters_name: NULL
---



```{r, include=FALSE}
# Get wd ------------------------------------------------------------------

setwd(rprojroot::find_rstudio_root_file())

# Load config -------------------------------------------------------------

source("local.config.R")
source("config.R")

# Read parameters ---------------------------------------------------------

source("parameters.R")

# Define parameters ---------------------------------------------------------

#param <- parameters[["test1"]]
param <- parameters[[params$parameters_name]]

# Import results ----------------------------------------------------------
pop_dt <- readRDS(file = file.path(folders$p_data,param$simulation_name, "population_data.rds"))
counts_dt <- readRDS(file = file.path(folders$p_data,param$simulation_name, "daily_counts.rds"))
summary_daily_counts <- readRDS(file = file.path(folders$p_data,param$simulation_name, "summary_daily_counts.rds"))
cc_dt <- readRDS(file = file.path(folders$p_data,param$simulation_name, "case_control_data.rds"))
transition_dt <- readRDS(file = file.path(folders$p_data,param$simulation_name, "transition_dt.rds"))
summary_transition_dt <- readRDS(file = file.path(folders$p_data,param$simulation_name, "summary_transition_dt.rds"))
  

# Colors ----------------------------------------------------------
mycolors <- c("#4B556B","#C16069","#E89F1B","#8698BF","#F07B87","#BEA372")

# Theme ----------------------------------------------------------
theme_plot <- theme(# Background completely blank
                    plot.background  = element_blank(),
                    panel.background = element_blank(),
                    panel.grid       = element_blank(),
                    # Only x and y axis lines visible, in black
                    axis.line        = element_line(colour = "black"),
                    axis.ticks       = element_line(colour = "black"),
                    axis.text        = element_text(colour = "black"),
                    axis.title       = element_text(colour = "black"),
                    # Legend
                    legend.background = element_blank(),
                    legend.key        = element_blank(),
                    legend.position   = "top",
                    legend.title = element_blank(),
                    # Title
                    plot.title = element_text(face = "bold"))
theme_facet <- theme_plot +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5),
        strip.background = element_rect(colour = "black", fill = NA),
        strip.text = element_text(face = "bold"))

# n pages for facets --------------------------------------------
n_col <- 4
n_row <- 4
n_runs_print <- n_col*n_row   # for the total number of runs = param$n_runs
n_pages <- ceiling(n_runs_print/(n_col*n_row))


```


# Scenario: `r param$simulation_name`

`r param$simulation_desc`

```{r scenario-info, echo = FALSE}
scenario_info <- data.frame(
  Parameter = c(
    # Population
    "Population size",
    "Simulation length",
    # Vaccination
    "Vaccination coverage",
     "Vaccination start day",
     "Vaccination length (days)",
     "Daily vaccination quota",
    # Infections
    "Reproduction number variant A",
    "Relative advantage of variant B over A",
    "Initial infected variant A",
    "Time of introduction of variant A",
    "Initial infected variant B",
    "Time of introduction of variant B",
    # Recovery
    "Recovery rate",
    # Vaccine effectiveness
    "VE against variant A",
    "VE against variant B",
    "Vaccine waning rate against variant A",
    "Vaccine waning rate against variant B",
    "Ramp-up period",
    # CC study
    "Number of controls per case"
    ),
  
  Value = c(param$N,
            param$sim_length,
            scales::percent(param$vacc_cov),
            param$vacc_start,
            param$vacc_length,
            round(param$vacc_cov * param$N / param$vacc_length),
            param$R_A,
            param$rel_RB,
            param$I0_A,
            param$T0_A,
            param$I0_B,
            param$T0_B,
            param$recov_rate,
            param$VE_A,
            param$VE_B,
            param$WA,
            param$WB,
            param$d,
            param$n_controls),
  group = c(
    rep(param$simulation_name,2),
    rep("Vaccination",4),
    rep("Infections",6),
    rep("Recovery",1),
    rep("Vaccine effectiveness",5),
    rep("Case-control study",1)
  ))
            
tab_scenario_info <- gt(scenario_info, groupname_col = "group") %>%
  tab_header(title    = "Simulation parameters") %>%
  cols_label(Parameter = "Parameter",
             Value     = "Value") %>%
  cols_align(align   = "left",   columns = Parameter) %>%
  cols_align(align   = "center", columns = Value) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_column_labels()) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_title()) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_row_groups()) %>%
  tab_options(
    table.border.top.style    = "hidden",
    table.border.bottom.style = "hidden",
    column_labels.border.bottom.width = px(1),
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color    = "black",
    table.font.size  = px(12),
    table.width      = pct(70))

tab_scenario_info
```


## Infections

::: {.panel-tabset}

### Overall

```{r inf-info-overall, echo = FALSE}
inf_info <- counts_dt[
  ,
  .(
    inf_A = max(cum_inf_A),
    inf_B = max(cum_inf_B)
  ),
  by = run_id
][
  ,
  `:=`(
    inf  = inf_A + inf_B,
    ar   = (inf_A + inf_B) / param$N * 100,
    ar_A = inf_A / param$N * 100,
    ar_B = inf_B / param$N * 100
  )
]


# summarise
summary_inf_info <- melt(
  inf_info,
  id.vars     = "run_id",
  variable.name = "measure",
  value.name  = "value"
)[
  ,
  .(
    median = median(value),
    p25    = quantile(value, 0.25),
    p75    = quantile(value, 0.75),
    min    = min(value),
    max    = max(value)
  ),
  by = measure
]

values <- c("inf","ar","inf_A","ar_A","inf_B","ar_B")
labels <- c("Total infected","Total attack rate (%)","Total infected variant A","Attack rate variant A (%)","Total infected variant B","Attack rate variant B (%)")
summary_inf_info$measure <- factor(summary_inf_info$measure, levels = values, labels = labels)
setorder(summary_inf_info, measure)
summary_inf_info$group <- c(rep("Overall", 2),rep("Variant A", 2),rep("Variant B", 2))

tab_inf_info_overall <- gt(arrange(summary_inf_info,measure), groupname_col = "group") %>%
  tab_header(title = "Simulation results") %>%
  cols_label(measure = " ") %>%
  cols_align(align = "center") %>%
  cols_align(align = "left",   columns = measure) %>%
  tab_style(style = cell_text(weight = "bold"),locations = cells_column_labels()) %>%
  tab_style(style = cell_text(weight = "bold"),locations = cells_title()) %>%
  tab_style(style = cell_text(weight = "bold"),locations = cells_row_groups()) %>%
  tab_options(
    table.border.top.style    = "hidden",
    table.border.bottom.style = "hidden",
    column_labels.border.bottom.width = px(1),
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color    = "black",
    table.font.size  = px(12),
    table.width = pct(70))

tab_inf_info_overall

```

### Individual runs

::: {.overflow-auto style="max-height:400px; overflow-x:auto;"}

```{r inf-info, echo = FALSE}
tab_inf_info <- gt(inf_info) %>%
  tab_header(title    = "Simulation results") %>%
  cols_label(run_id = "Run id",
             inf = "Total infected",
             inf_A = "Total infected variant A",
             inf_B = "Total infected variant B",
             ar = "Total attack rate (%)",
             ar_A = "Attack rate variant A (%)",
             ar_B = "Attack rate variant B (%)") %>%
  cols_align(align = "center") %>%
  cols_align(align = "left",   columns = run_id) %>%
  tab_style(style = cell_text(weight = "bold"),locations = cells_column_labels()) %>%
  tab_style(style = cell_text(weight = "bold"),locations = cells_title()) %>%
  tab_options(
    table.border.top.style    = "hidden",
    table.border.bottom.style = "hidden",
    column_labels.border.bottom.width = px(1),
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color    = "black",
    table.font.size  = px(12))

tab_inf_info

```

:::

:::

::: {.panel-tabset}

### New infections

::: {.panel-tabset}

#### Overall

```{r inf-overall-plot, echo = FALSE}

ggplot(summary_daily_counts, aes(x = time)) +
  geom_line(aes(y = new_inf_A_median, color = "Variant A"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = new_inf_A_p25, ymax = new_inf_A_p75), fill = mycolors[3],alpha = 0.5) +
  geom_line(aes(y = new_inf_B_median, color = "Variant B"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = new_inf_B_p25, ymax = new_inf_B_p75),fill = mycolors[4],alpha = 0.5) +
  labs(title = "New infections by virus variant over time  (Median; IQR)",
       x = "Time (days)",
       y = "Number of new cases") +
  scale_color_manual(values = c(mycolors[3], mycolors[4])) +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) + 
  theme_plot

```

#### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r inf-plot, echo = FALSE}

for (i in seq_len(n_pages)) {

  p <- ggplot(counts_dt, aes(x = time)) +
  geom_line(aes(y = new_inf_A, color = "Variant A"), linewidth = 0.8) +
  geom_line(aes(y = new_inf_B, color = "Variant B"), linewidth = 0.8) +
  labs(title = paste0("New infections by virus variant over time (",i,")"),
       x = "Time (days)",
       y = "Number of new cases") +
  scale_color_manual(values = c(mycolors[3],mycolors[4])) +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) + 
  theme_facet +
  facet_wrap_paginate(
    ~ run_id,
    ncol = n_col,
    nrow = n_row,
    page = i)
  print(p)
}

```

:::

:::


### Cumulative infections

::: {.panel-tabset}

#### Overall

```{r cum-inf-overall-plot, echo = FALSE}

ggplot(summary_daily_counts, aes(x = time)) +
  geom_line(aes(y = cum_inf_A_median, color = "Variant A"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = cum_inf_A_p25, ymax = cum_inf_A_p75), fill = mycolors[3],alpha = 0.5) +
  geom_line(aes(y = cum_inf_B_median, color = "Variant B"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = cum_inf_B_p25, ymax = cum_inf_B_p75),fill = mycolors[4],alpha = 0.5) +
  labs(title = "Cumulative number of infections by virus variant over time  (Median; IQR)",
       x = "Time (days)",
       y = "Number of new cases") +
  scale_color_manual(values = c(mycolors[3], mycolors[4])) +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) + 
  theme_plot

```

#### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r cum-inf-plot, echo = FALSE}

for (i in seq_len(n_pages)) {
p <- ggplot(counts_dt, aes(x = time)) +
  geom_line(aes(y = cum_inf_A, color = "Variant A"), linewidth = 0.8) +
  geom_line(aes(y = cum_inf_B, color = "Variant B"), linewidth = 0.8) +
  labs(title = paste0("Cumulative number of infections by virus variant over time (",i,")"),
       x = "Time (days)",
       y = "Number of new cases") +
  scale_color_manual(values = c(mycolors[3],mycolors[4])) +
  scale_x_continuous(expand = c(0,0), breaks = c(1,seq(50,max(counts_dt$time),50))) + 
  scale_y_continuous(expand = c(0,0)) + 
  facet_wrap_paginate(~run_id,
    ncol = n_col,
    nrow = n_row,
    page = i) +
  theme_facet 
  
  print(p)
}

```

:::

::: 

### Prevalence of infections

::: {.panel-tabset}

#### Overall

```{r prev-inf-overall-plot, echo = FALSE}

ggplot(summary_daily_counts, aes(x = time)) +
  geom_line(aes(y = nIA_median, color = "Variant A"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = nIA_p25, ymax = nIA_p75), fill = mycolors[3],alpha = 0.5) +
  geom_line(aes(y = nIB_median, color = "Variant B"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = nIB_p25, ymax = nIB_p75),fill = mycolors[4],alpha = 0.5) +
  labs(title = "Prevalence of infections by virus variant over time  (Median; IQR)",
       x = "Time (days)",
       y = "Number of cases") +
  scale_color_manual(values = c(mycolors[3], mycolors[4])) +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) + 
  theme_plot

```

#### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r prev-inf-plot, echo = FALSE}
for (i in seq_len(n_pages)) {
 p <- ggplot(counts_dt, aes(x = time)) +
  geom_line(aes(y = nIA, color = "Variant A"), linewidth = 0.8) +
  geom_line(aes(y = nIB, color = "Variant B"), linewidth = 0.8) +
  labs(title = paste0("Prevalence of infections by virus variant over time (",i,")"),
       x = "Time (days)",
       y = "Number of cases") +
  scale_color_manual(values = c(mycolors[3],mycolors[4])) +
  scale_x_continuous(expand = c(0,0), breaks = c(1,seq(50,max(counts_dt$time),50))) + 
  scale_y_continuous(expand = c(0,0)) +
  theme_facet +
  facet_wrap_paginate(
    ~ run_id,
    ncol = n_col,
    nrow = n_row,
    page = i)

  print(p)
}

```

:::

:::

:::



## Susceptibles

::: {.panel-tabset}

### Overall

```{r sus-overall-plot, echo = FALSE}

ggplot(summary_daily_counts, aes(x = time)) +
  geom_line(aes(y = nS_naive_median), color = mycolors[1], linewidth = 0.8) +
  geom_ribbon(aes(ymin = nS_naive_p25, ymax = nS_naive_p75), fill = mycolors[1],alpha = 0.5) +
  labs(title = "Number of susceptible individuals (S = NI - R - V) over time  (Median; IQR)",
       x = "Time (days)",
       y = "Number of individuals") +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  theme_plot

```

### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r sus-plot, echo = FALSE}
for (i in seq_len(n_pages)) {
 p <- ggplot(counts_dt, aes(x = time)) +
  geom_line(aes(y = nS - (nR+nV)), color = mycolors[1], linewidth = 0.8) +
  labs(title = paste0("Number of susceptible individuals (S = NI - R - V) (",i,")"),
       x = "Time (days)",
       y = "Number of individuals") +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0), limits = c(0, max(counts_dt$nS))) +
  theme_facet +
  facet_wrap_paginate(
    ~ run_id,
    ncol = n_col,
    nrow = n_row,
    page = i)

  print(p)
}

```

::: 

:::


## Recovered

::: {.panel-tabset}

### New recoveries

::: {.panel-tabset}

#### Overall

```{r rec-overall-plot, echo = FALSE}

ggplot(summary_daily_counts, aes(x = time)) +
  geom_line(aes(y = new_rec_median), color = mycolors[1], linewidth = 0.8) +
  geom_ribbon(aes(ymin = new_rec_p25, ymax = new_rec_p75), fill = mycolors[1], alpha = 0.5) +
  labs(title = "Number of new recoveries over time (Median; IQR)",
       x = "Time (days)",
       y = "Number of individuals") +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  theme_plot

```


#### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r rec-plot, echo = FALSE}
for (i in seq_len(n_pages)) {
 p <- ggplot(counts_dt, aes(x = time)) +
  geom_line(aes(y = new_rec), color = mycolors[1], linewidth = 0.8) +
  labs(title = paste0("Number of new recoveries (",i,")"),
       x = "Time (days)",
       y = "Number of individuals") +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  theme_facet +
  facet_wrap_paginate(
    ~ run_id,
    ncol = n_col,
    nrow = n_row,
    page = i)

  print(p)
}
```

:::

::: 

### Cumulative recoveries

::: {.panel-tabset}

#### Overall

```{r cum-rec-overall-plot, echo = FALSE}

ggplot(summary_daily_counts, aes(x = time)) +
  geom_line(aes(y = nR_median), color = mycolors[1], linewidth = 0.8) +
  geom_ribbon(aes(ymin = nR_p25, ymax = nR_p75), fill = mycolors[1], alpha = 0.5) +
  labs(title = "Number of new recoveries over time (Median; IQR)",
       x = "Time (days)",
       y = "Number of individuals") +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  theme_plot

```


#### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r cum-rec-plot, echo = FALSE}
for (i in seq_len(n_pages)) {
 p <- ggplot(counts_dt, aes(x = time)) +
  geom_line(aes(y = nR), color = mycolors[1], linewidth = 0.8) +
  labs(title = paste0("Number of cumulative recoveries (",i,")"),
       x = "Time (days)",
       y = "Number of individuals") +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  theme_facet +
  facet_wrap_paginate(
    ~ run_id,
    ncol = n_col,
    nrow = n_row,
    page = i)

  print(p)
}
```

::: 

:::

:::


## Variant proportion

::: {.panel-tabset}

### Overall

```{r variant-prop-info, echo = FALSE}
# Prepare data for table
long_dt <- melt(summary_transition_dt, measure.vars = patterns("_median$|_p25$|_p75$|_min$|_max$"))
long_dt <- long_dt[, c("measure", "stat") := tstrsplit(variable, "_(?=[^_]+$)", perl = TRUE)]
var_prop_info <- dcast(long_dt, measure ~ stat, value.var = "value")[, .(measure, median, p25, p75, min, max)]

values <- c("days_to_dominance","days_to_A_gone","day_B_intro","day_B_dominant","day_A_gone")
labels <- c("Number of days until B dominates","Number of days until A disappears","Day of B introduction","Day of B dominance","Day of A disappearance")
var_prop_info$measure <- factor(var_prop_info$measure, levels = values, labels = labels)

setorder(var_prop_info, measure)

tab_prop_info <- gt(var_prop_info) %>%
  tab_header(title = "Simulation results") %>%
  cols_label(measure = " ") %>%
  cols_align(align = "center") %>%
  cols_align(align = "left",   columns = measure) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_column_labels()) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_title()) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_row_groups()) %>%
  tab_options(
    table.border.top.style    = "hidden",
    table.border.bottom.style = "hidden",
    column_labels.border.bottom.width = px(1),
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color    = "black",
    table.font.size  = px(12))

tab_prop_info

```

### Individual runs

```{r variant-prop-ind, echo = FALSE}

# Prepare data for table
tab_prop_info <- gt(transition_dt) %>%
  tab_header(title    = "Simulation results") %>%
  cols_label(run_id = "Run id",
             days_to_dominance = "Number of days until B dominates",
             days_to_A_gone = "Number of days until A disappears",
             day_B_intro = "Day of B introduction",
             day_B_dominant = "Day of B dominance",
             day_A_gone = "Day of A disappearance") %>%
  cols_align(align = "center") %>%
  cols_align(align = "left",   columns = run_id) %>%
  tab_style(style = cell_text(weight = "bold"),locations = cells_column_labels()) %>%
  tab_style(style = cell_text(weight = "bold"),locations = cells_title()) %>%
  tab_options(
    table.border.top.style    = "hidden",
    table.border.bottom.style = "hidden",
    column_labels.border.bottom.width = px(1),
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color    = "black",
    table.font.size  = px(12))

tab_prop_info

```

:::

::: {.panel-tabset}

### Line plot

::: {.panel-tabset}

#### Overall

```{r var-prop-overall, echo = FALSE}

# Proportion of variant A and variant B
ggplot(summary_daily_counts, aes(x = time)) +
  geom_line(aes(y = prop_A_median*100, color = "Variant A"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = prop_A_p25*100, ymax = prop_A_p75*100), fill = mycolors[4], alpha = 0.5) +
  geom_line(aes(y = prop_B_median*100, color = "Variant B"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = prop_B_p25*100, ymax = prop_B_p75*100), fill = mycolors[3], alpha = 0.5) +
  labs(title = paste0("Variant proportion over time (Median;IQR)"),
       x = "Time (days)",
       y = "Variant proportion (%)") +
  scale_color_manual(values = c(mycolors[4],mycolors[3])) +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  theme_plot


```


#### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r var-prop, echo = FALSE}

# Proportion of variant A and variant B

for (i in seq_len(n_pages)) {
  
 p <- ggplot(counts_dt, aes(x = time)) +
  geom_line(aes(y = prop_A*100, color = "Variant A"), linewidth = 0.8) +
  geom_line(aes(y = prop_B*100, color = "Variant B"), linewidth = 0.8) +
  labs(title = paste0("Variant proportion over time (",i,")"),
       x = "Time (days)",
       y = "Variant proportion (%)") +
  scale_color_manual(values = c(mycolors[4],mycolors[3])) +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  theme_facet +
  facet_wrap_paginate(
    ~ run_id,
    ncol = n_col,
    nrow = n_row,
    page = i)

  print(p)
}


```

:::

:::

### Area plot

::: {.panel-tabset}

#### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r var-prop-bar, echo = FALSE}

# reshape to long format
plot_dt <- melt(
  counts_dt,
  id.vars = c("run_id", "time"),
  measure.vars = c("prop_A", "prop_B"),
  variable.name = "variant",
  value.name = "proportion"
)

# rename labels
plot_dt[, variant := factor(
  variant,
  levels = c("prop_A", "prop_B"),
  labels = c("Variant A", "Variant B")
)]

# area plot
for (i in seq_len(n_pages)) {
 p <- ggplot(plot_dt, aes(x = time, y = proportion*100, fill = variant)) +
  geom_area(position = "fill", alpha = 0.8) +
  labs(title = paste0("Variant proportion over time (",i,")"),
       x = "Time (days)",
       y = "Variant proportion (%)") +
  scale_fill_manual(values = c(mycolors[4],mycolors[3])) +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  theme_facet +
  facet_wrap_paginate(
    ~ run_id,
    ncol = n_col,
    nrow = n_row,
    page = i)

  print(p)
}

```

:::

::: 

:::

## Vaccination

```{r vacc-info, echo = FALSE}
vacc_info <- data.frame(
  measure = c("Vaccination coverage target (%)",
              "Vaccination coverage (%)",
              "Vaccination target",
              "Total vaccinated"),
  value = c(param$vacc_cov*100,
            round(max(counts_dt$nV)/param$N*100,1),
            param$vacc_cov * param$N,
            max(counts_dt$nV)))
            
tab_vacc_info <- gt(vacc_info) %>%
  tab_header(title    = "Simulation results") %>%
  cols_label(measure = "Measure",value     = "Value") %>%
  cols_align(align   = "left",   columns = measure) %>%
  cols_align(align   = "center", columns = value) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_column_labels()) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_title()) %>%
  tab_options(table.border.top.style    = "hidden",
              table.border.bottom.style = "hidden",
              column_labels.border.bottom.width = px(1),
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color    = "black",
              table.font.size  = px(12),
              table.width = pct(70))

tab_vacc_info

```


```{r vacc-plot, echo = FALSE}

ggplot(subset(counts_dt, run_id == 1), aes(x = time)) +
  geom_line(aes(y = nV), color = mycolors[1], linewidth = 0.8) +
  labs(title = "Vaccination over time (first run)",
       x = "Time (days)",
       y = "Number of individuals") +
  scale_x_continuous(expand = c(0,0), breaks = c(1,seq(50,max(counts_dt$time),50))) + 
  scale_y_continuous(expand = c(0,0), limits = c(0, max(counts_dt$nV)*1.2))+
  # add info to the plot
  geom_vline(xintercept = param$vacc_start, color = mycolors[2], linetype = "dashed") +
  geom_vline(xintercept = param$vacc_start+param$vacc_length, color = mycolors[2], linetype = "dashed") +
  # total vaccinated
  # geom_hline(yintercept = param$vacc_cov*param$N, color = mycolors[2], linetype = "dashed") +
  # geom_hline(yintercept = max(counts_dt$nV), color = mycolors[1], linetype = "dashed") +
  # annotate("text", x = 1, y = param$vacc_cov * param$N * 1.05,
  #          label = paste0("Target: ", param$vacc_cov * param$N),
  #          hjust = 0, colour = mycolors[2], size = 3.5) +
  # annotate("text", x = 1, y = max(counts_dt$nV) * 0.95,
  #          label = paste0("Vaccinated: ", max(counts_dt$nV)),
  #          hjust = 0, colour = mycolors[1], size = 3.5) +
  theme_facet

```


## Average protection 

::: {.panel-tabset}

#### Overall

```{r prot-overall-plot, echo = FALSE}

ggplot(summary_daily_counts, aes(x = time)) +
  geom_line(aes(y = avg_prot_A_median, color = "Variant A"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = avg_prot_A_p25, ymax = avg_prot_A_p75), fill = mycolors[4], alpha = 0.5) +
  geom_line(aes(y = avg_prot_B_median, color = "Variant B"), linewidth = 0.8) +
  geom_ribbon(aes(ymin = avg_prot_B_p25, ymax = avg_prot_B_p75), fill = mycolors[3], alpha = 0.5) +
  labs(title = "Average protection by virus variant over time (Median; IQR)",
       x = "Time (days)",
       y = "Number of individuals") +
  scale_color_manual(values = c(mycolors[4],mycolors[3])) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
   # add vacc info to the plot
  geom_vline(xintercept = param$vacc_start, color = mycolors[1], linetype = "dashed") +
  geom_vline(xintercept = param$vacc_start+param$vacc_length, color = mycolors[1], linetype = "dashed") +
  geom_vline(xintercept = param$vacc_start+param$vacc_length+14, color = mycolors[1], linetype = "dashed") +
  theme_plot

```


#### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r prot-plot, echo = FALSE}
for (i in seq_len(n_pages)) {

  p <- ggplot(counts_dt, aes(x = time)) +
  geom_line(aes(y = avg_prot_A, color = "Variant A"), linewidth = 0.8) +
  geom_line(aes(y = avg_prot_B, color = "Variant B"), linewidth = 0.8) +
  labs(title = paste0("Average protection by virus variant over time (",i,")"),
       x = "Time (days)",
       y = "Average probability of protection") +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) + 
  scale_color_manual(values = c(mycolors[4],mycolors[3])) +
 # add vacc info to the plot
  geom_vline(xintercept = param$vacc_start, color = mycolors[1], linetype = "dashed") +
  geom_vline(xintercept = param$vacc_start+param$vacc_length, color = mycolors[1], linetype = "dashed") +
  geom_vline(xintercept = param$vacc_start+param$vacc_length+14, color = mycolors[1], linetype = "dashed") +
  theme_facet +
  facet_wrap_paginate(
    ~ run_id,
    ncol = n_col,
    nrow = n_row,
    page = i)

  print(p)
}
```

::: 

:::

# Case-control study data

## Number of cases and controls

::: {.panel-tabset}

### Overall

::: {.overflow-auto style="max-height:400px; overflow-x:auto;"}

```{r cc-summary-info, echo = FALSE}
# Get all tsv_30 levels except "Unvaccinated"
tsv_levels <- setdiff(levels(cc_dt$tsv_30), "Unvaccinated")

# Run aggregation
summary_cc_counts <- cc_dt[, {
  
  # Base counts
  base <- list(
    Cases                   = sum(cc == "case",                                                  na.rm = TRUE),
    Controls                = sum(cc == "control",                                               na.rm = TRUE),
    `Vaccinated cases`      = sum(cc == "case"    & vaccinated_f == "Vaccinated",                na.rm = TRUE),
    `Unvaccinated cases`    = sum(cc == "case"    & vaccinated_f == "Unvaccinated",              na.rm = TRUE),
    `Vaccinated controls`   = sum(cc == "control" & vaccinated_f == "Vaccinated",                na.rm = TRUE),
    `Unvaccinated controls` = sum(cc == "control" & vaccinated_f == "Unvaccinated",              na.rm = TRUE)
  )
  
  # Base variant A counts
  base_a <- list(
    `Cases A`               = sum(cc == "case" & variant == "A",                                 na.rm = TRUE),
    `Cases A unvaccinated`  = sum(cc == "case" & variant == "A" & vaccinated_f == "Unvaccinated",na.rm = TRUE),
    `Cases A vaccinated`    = sum(cc == "case" & variant == "A" & vaccinated_f == "Vaccinated",  na.rm = TRUE)
  )
  
  # Dynamic tsv counts for variant A
  tsv_a <- setNames(
    lapply(tsv_levels, function(lvl)
      sum(cc == "case" & variant == "A" & vaccinated_f == "Vaccinated" & as.character(tsv_30) == lvl, na.rm = TRUE)
    ),
    paste0("Cases A vaccinated ", tsv_levels)
  )
  
  # Base variant B counts
  base_b <- list(
    `Cases B`               = sum(cc == "case" & variant == "B",                                 na.rm = TRUE),
    `Cases B unvaccinated`  = sum(cc == "case" & variant == "B" & vaccinated_f == "Unvaccinated",na.rm = TRUE),
    `Cases B vaccinated`    = sum(cc == "case" & variant == "B" & vaccinated_f == "Vaccinated",  na.rm = TRUE)
  )
  
  # Dynamic tsv counts for variant B
  tsv_b <- setNames(
    lapply(tsv_levels, function(lvl)
      sum(cc == "case" & variant == "B" & vaccinated_f == "Vaccinated" & as.character(tsv_30) == lvl, na.rm = TRUE)
    ),
    paste0("Cases B vaccinated ", tsv_levels)
  )
  
  c(base, base_a, tsv_a, base_b, tsv_b)
  
}, by = run_id]


# summarise
summary_cc <- melt(
  summary_cc_counts,
  id.vars     = "run_id",
  variable.name = "measure",
  value.name  = "value"
)[
  ,
  .(
    median = median(value),
    p25    = quantile(value, 0.25),
    p75    = quantile(value, 0.75),
    min    = min(value),
    max    = max(value)
  ),
  by = measure
][, group := c(
    rep("Overall",   6),
    rep("Variant A", 3 + length(tsv_levels)),
    rep("Variant B", 3 + length(tsv_levels))
)]

tab_cc_overall_info <- gt(summary_cc, groupname_col = "group") %>%
  tab_header(title    = "Simulation results") %>%
  cols_label(measure = " ") %>%
  cols_align(align = "center") %>%
  cols_align(align = "left",   columns = measure) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_column_labels()) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_title()) %>%
  tab_style(style     = cell_text(weight = "bold"),locations = cells_row_groups()) %>%
  tab_options(
    table.border.top.style    = "hidden",
    table.border.bottom.style = "hidden",
    column_labels.border.bottom.width = px(1),
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color    = "black",
    table.font.size  = px(12),
    table.width = pct(70))

tab_cc_overall_info

```

:::

### Individual runs

::: {.overflow-auto style="max-height:400px; overflow-x:auto;"}

```{r cc-info, echo = FALSE}
            
tab_cc_info <- gt(summary_cc_counts) %>%
  tab_header(title    = "Simulation results") %>%
  cols_label(run_id = "Run id") %>%
  cols_align(align = "center") %>%
  cols_align(align = "left",   columns = run_id) %>%
  tab_style(style = cell_text(weight = "bold"),locations = cells_column_labels()) %>%
  tab_style(style = cell_text(weight = "bold"),locations = cells_title()) %>%
  tab_options(table.border.top.style    = "hidden",
              table.border.bottom.style = "hidden",
              column_labels.border.bottom.width = px(1),
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color    = "black",
              table.font.size  = px(12))

tab_cc_info

```

:::

:::

## Cases and controls over time

```{r summary_cc_dt, echo = FALSE}
# Cases and controls by run_id
n_cc <- cc_dt[
  ,
  .(n = .N),
  by = .(run_id, t, cc)
][
  ,
  label := cc
]

# Vaccinated by case/control by run_id
n_cc_vac <- cc_dt[
  vaccinated == 1,
  .(n = .N),
  by = .(run_id, tv, cc)
][
  ,
  label := paste0("Vaccinated ", cc)
]

# Median cases/controls 
n_cc_summary <- n_cc[
  ,
  .(
    median_n = as.numeric(median(n)),
    p25_n = as.numeric(quantile(n, 0.25)),
    p75_n = as.numeric(quantile(n, 0.75))
  ),
  by = .(t, cc, label)
]

# Median vaccinated by case/control
n_cc_vac_summary <- n_cc_vac[
  ,
  .(
    median_n = as.numeric(median(n)),
    p25_n = as.numeric(quantile(n, 0.25)),
    p75_n = as.numeric(quantile(n, 0.75))
  ),
  by = .(tv, cc, label)
]

```

::: {.panel-tabset}

### Overall

```{r cc-overall-plot, echo = FALSE}

ggplot() +
  geom_line(data = n_cc_summary, aes(x = t, y = median_n, color = label, group = label), linewidth = 0.8, linetype = "solid") +
  geom_ribbon(data = n_cc_summary, aes(x = t, ymin = p25_n, ymax = p75_n, fill = label, group = label), alpha = 0.5) +
  geom_line(data = n_cc_vac_summary, aes(x = tv, y = median_n, color = label, group = label), linewidth = 0.8, linetype = "dashed") +
  geom_ribbon(data = n_cc_vac_summary, aes(x = tv, ymin = p25_n, ymax = p75_n, fill = label, group = label), alpha = 0.5) +
  labs(title = paste0("Cases and controls and vaccination over time (Median;IQR)"),
       x = "Time of infection / vaccination (days)",
       y = "Number of individuals") +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) + 
  scale_color_manual(values = c("case" = mycolors[2], "control" = mycolors[1], "Vaccinated case" = mycolors[2], "Vaccinated control" = mycolors[1])) +
  scale_fill_manual(values = c("case" = mycolors[2], "control" = mycolors[1], "Vaccinated case" = mycolors[2], "Vaccinated control" = mycolors[1])) +
  theme_plot

```

### Individual runs

::: {.overflow-auto style="max-height:500px; overflow-x:auto;"}

```{r cc-plot, echo = FALSE}

for (i in seq_len(n_pages)) {

p <- ggplot() +
  geom_line(data = n_cc, aes(x = t, y = n, color = label, group = label), linewidth = 0.8, linetype = "solid") +
  geom_line(data = n_cc_vac, aes(x = tv, y = n, color = label, group = label), linewidth = 0.8, linetype = "dashed") +
  labs(title = paste0("Cases and controls and vaccination over time (",i,")"),
       x = "Time of infection / vaccination (days)",
       y = "Number of individuals") +
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) + 
  scale_color_manual(values = c(mycolors[1],mycolors[2],mycolors[1],mycolors[2])) +
  theme_facet +
  facet_wrap_paginate(
    ~ run_id,
    ncol = n_col,
    nrow = n_row,
    page = i)

  print(p)
}

```

:::

::: 
